Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex

\subsubsection{Image Acquisition}
While the automobile detection subsystem correctly identifies when a vehicle enters the lot, the image acquisition subsystem is responsible for determining when to capture a picture of that car in order to optimize the quality of the license plate image. The timing difference between when the Raspberry Pi receives the signal from the Arduino Fio and when the image is captured is set to 500 milliseconds so as to allow the car to completely pass the Arduino Fio and enter the capture area. Only one picture is taken of each car so that capture time and power consumption on the Raspberry Pi are limited. This allows for more resources to be allocated towards the process of image processing.

\subsubsection{Image Processing}
Once the image is captured, the Raspberry Pi will then focus on detecting the license plate in the image and cropping the image to only include the license plate. This will be done in order to minimize the size of the transmission and the power required for that transmission. In order to detect the location of the license plate within the larger image, a detection algorithm needs to be applied.

The location of the license plates will be detected on the acquisition Raspberry Pi using the OpenCV (Open Source Computer Vision Library) API \cite{openCV}, which provides many different algorithms that can be used for image detection and shape recognition. This particular API was chosen for both its ease of use and widespread cross-compatibility; it has interfaces for development in C, C++, Python, Java, and MATLAB, and supports all major operating systems (including distributions of Linux such as Raspbian). Because OpenCV is used across the industry for image processing, we are confident that it will meet our needs.

Once the OpenCV software has detected the license plate, the image will then be cropped as needed until all that remains in the image is the license plate from the car that is entering the lot. That image will then be sent to the central base station via an XBee radio transmission.

@@

\section{Results}
\subsection{ALPR Results}
Three data sets were run through each ALPR system. In each case, Intrada ALPR was able to recognize at least twice as many plates as OpenALPR.

@@

Taylor Sallee wrote all code for the web application, excluding the front-end "Smartlots" part of the site that was already in place before the start of this project. Roy Stilwell from the ACMx group wrote the code for that part of the site. Taylor's contribution was the entire administrator interface, the RESTful API that services the website and the Raspberry Pis when they make POST requests. He also added user authentication and PHP security to all sensitive routes created the database tables for all data that our group was adding (images, licenses, intrada_licenses, users), and wrote all code for viewing, creating, updating, and deleting data in these tables. He collaborated with Andrew Koelling to write the base-station Python code that listens for data from the Arduino Fios and Raspberry Pis, and sends that data to the server via HTTP requests. Some of this code was in place before the project, but Taylor and Andrew refactored almost all of it, and added in the parts to handle the image data, and the part that differentiates the Arduino Fio data from the Raspberry Pi (image) data. Taylor also worked with Santiago and Kevin on the sensor Raspberry Pis, making sure that everything was installed correctly, and testing the top-to-bottom functionality of the system (that is, make sure data is getting from the sensors all the way to the web application). Taylor's work is described in sections 3.3, 3.5, and 4.3.

>>>>

\subsubsection{Image Acquisition}
While the automobile detection subsystem correctly identifies when a vehicle enters the lot, the image acquisition subsystem is responsible for determining when to capture a picture of that car in order to optimize the quality of the license plate image. The timing difference between when the Raspberry Pi receives the signal from the Arduino Fio and when the image is captured is set to 500 milliseconds so as to allow the car to completely pass the Arduino Fio and enter the capture area. Only one picture is taken of each car so that capture time and power consumption on the Raspberry Pi are limited. This frees up more resources to be allocated towards the process of image processing.

\subsubsection{Image Processing}
Once an image is captured, the Raspberry Pi creates a subprocess which processes the captured image. The image is processed using the OpenCV (Open Source Computer Vision Library) API \cite{openCV}. This API provides many different algorithms that can be used for image detection and shape recognition. It was chosen for both its ease of use and widespread cross-compatibility; it has interfaces for development in C, C++, Python, Java, and MATLAB, and supports all major operating systems (including distributions of Linux such as Raspbian).

When processing the image, two factors are taken into consideration:
\begin{enumerate}
\item File Size and
\item License Plate Quality
\end{enumerate}
The file size is reduced as much as possible in order to expedite the file transfer process from the Acquisition Raspberry Pi. The second factor, license plate quality, is considered because the image must be readable by the Optical Character Recognition (OCR) software used on the server. Several different methods of processing the images using OpenCV were attempted, including but not limited to:
\begin{enumerate}
\item Contour Mapping,
\item Image Cropping,
\item Image Resizing and Compression, and
\item Color Manipulation
\end{enumerate}

Two datasets are analyzed on how they ran through the OCR software (section 4.2). These two datasets, "cropped images" and "compressed images" had different methods of processing applied. "Cropped images" is a set of images that were greedily cropped to eliminate space at the top and bottom of the picture around the car and were converted to grayscale images. "Compressed images" is a set of images that had various amounts of compression applied to them as well as different color filters.

Once the software has processed the image is sent to the ACMx server via a wi-fi connection.

@@

\section{Results}

\subsection{Image Processing Results}

The original goal in image processing was to crop the image down from a large image to a small, manageable image of just the license plate. This software does exist, and is used in many applications, such as \cite{du2013} and \cite{e470}. However, this software is very hard to implement in practice. Most applications use contour mapping to detect the license plate, but this relies on having an image where the license plate is one of the prominent features in the image. When contour mapping methods were applied to the images in this project, most commonly the contours detected pebbles on the ground in the concrete or lines in the parking lot instead of license plates. While successful in other applications, it did not prove to be a good method in this instance.

With contour mapping out of the question, the chosen method for image processing was converting the image to grayscale, resizing it to reduce the file size, and then greedily cropping the top and bottom of the picture to eliminate the ground below the car and the sky above. While not 100\% effective, it proved to be the best solution in testing.

\subsection{ALPR Results}
Three data sets were run through each ALPR system. In each case, Intrada ALPR was able to recognize at least twice as many plates as OpenALPR.

@@

Taylor Sallee wrote all code for the web application, excluding the front-end "Smartlots" part of the site that was already in place before the start of this project. Roy Stilwell from the ACMx group wrote the code for that part of the site. Taylor's contribution was the entire administrator interface, the RESTful API that services the website and the Raspberry Pis when they make POST requests. He also added user authentication and PHP security to all sensitive routes created the database tables for all data that our group was adding (images, licenses, intrada\_licenses, users), and wrote all code for viewing, creating, updating, and deleting data in these tables. He collaborated with Andrew Koelling to write the base-station Python code that listens for data from the Arduino Fios and Raspberry Pis, and sends that data to the server via HTTP requests. Some of this code was in place before the project, but Taylor and Andrew refactored almost all of it, and added in the parts to handle the image data, and the part that differentiates the Arduino Fio data from the Raspberry Pi (image) data. Taylor also worked with Santiago and Kevin on the sensor Raspberry Pis, making sure that everything was installed correctly, and testing the top-to-bottom functionality of the system (that is, make sure data is getting from the sensors all the way to the web application). Taylor's work is described in sections 3.3, 3.5, and 4.3.
